Composition-climate paper

### 2015-07-29 Composition_Ecology.Rmd
Fixes to get the `clim_change` call to work.  There was an error in `climate_ts` because I forgot to change a period to an underscore.  `knitr` wasn't picking up that error, but instead showing me the inline code error further down.
+ `climate_ts` - changed `now.rast` to `rast_in`.

Output all `tiff` and `rds` files.

```{r figure1, fig.width=6, fig.height=5, echo = FALSE, warning = FALSE, message=FALSE}

@@

grid.arrange(climate_values$plot, land_use_plot, nrow=1, widths = c(3, 4))

@@

`r clim_change <- climate_values$modern$value - climate_values$past$value `

>>>>

```{r figure1, echo = FALSE, warning = FALSE, message=FALSE, fig.width=6, fig.height=5}

@@

clim_change <- climate_values$modern$value - climate_values$past$value

grid.arrange(climate_values$plot, land_use_plot, nrow=1, widths = c(3, 4))
```

@@
